Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-22 docs/manuscript/manuscript.tex
First Paragraph of Water Accessibility typology.

\subsection*{Water accessibility typologies}
\hl{Show the typology/cluster results and discuss.}
NBClust statistic analysis developed and determined four distinct groups. First cluster group composed of countries near the equator or in the Sub-Sahara Regions. The analysis of the second group represents countries considered developed or recently industrialized. Third cluster group represents most of the countries in the central Africa and may have similar factors as the first cluster group. The fourth cluster group represents most of countries in the middle east or predominately non-African countries. There is a great internally heterogeneous clusters for the 76 distinct countries. The cluster analysis' dendrogram is shown in \autoref{fig:dendrogram}, and the corresponding NBClust curve yielding the optimal four clusters is shown in \autoref{fig:optimal-clusters, fig:optimal-cuts}.

>>>>

\subsection*{Water accessibility typologies}
\hl{Show the typology/cluster results and discuss.}
NBClust statistic analysis developed and determined four distinct groups. First cluster group composed of countries near the equator or in the Sub-Sahara Regions. The analysis of the second group represents countries considered developed or recently industrialized. Third cluster group represents most of the countries in the central Africa and may have similar factors as the first cluster group. The fourth cluster group represents most of countries in the middle east or predominately non-African countries. There is a great internally heterogeneous clusters for the 76 distinct countries. The cluster analysis' dendrogram is shown in \autoref{fig:dendrogram}, and the corresponding NBClust curve yielding the optimal four clusters is shown in \autoref{fig:optimal-clusters}, \autoref{fig:optimal}. \autoref{}
